---
title: "MLH03"
author: "Liu Zhe"
date: "2022-11-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = TRUE,
  warning = FALSE
)
```

# Environment Variables and Packages

```{r}
options(java.parameters = "-Xmx2048m",
        stringsAsFactors = FALSE, 
        encoding = 'UTF-8')

suppressPackageStartupMessages({
  # ISLR2
  library(ISLR2)
  # Schmidt
  library(far)
  # kernel density
  library(ks)
  # DM
  library(zip)
  library(openxlsx)
  library(readxl)
  library(writexl)
  library(RcppRoll)
  library(plyr)
  library(stringi)
  library(feather)
  library(RODBC)
  library(MASS)
  library(car)
  library(data.table)
  library(lubridate)
  library(plotly)
  library(pROC)
  library(tidymodels)
  library(tidyverse)
})
```

# Auto

environment variables. 

```{r}
color.origin <- c('1' = '#19d3f3', '2' = '#FFB6C1', '3' = '#00FF00')
```

Scatter-plot matrix, or splom. 

```{r}
auto.splom <- plot_ly(ISLR2::Auto, 
                      color = as.integer(ISLR2::Auto$origin), 
                      colors = color.origin) %>% 
  add_trace(
    type = 'splom',
    dimensions = list(
      list(label = 'mpg', values = ~mpg), 
      list(label = 'cyl', values = ~cylinders), 
      list(label = 'displace', values = ~displacement), 
      list(label = 'hp', values = ~horsepower), 
      list(label = 'weight', values = ~weight), 
      list(label = 'acc', values = ~acceleration), 
      list(label = 'year', values = ~year), 
      list(label = 'origin', values = ~origin)
    ), 
    text = ~origin, 
    marker = list(
      size = 3
    )
  ) %>% 
  hide_colorbar() %>% 
  layout(
    title = 'Scatter-plot Matrix of Auto', 
    hovermode = 'closest', 
    dragmode = 'select', 
    plot_bgcolor = 'rgba(240,240,240, 0.95)', 
    autosize = TRUE, 
    xaxis = list(domain = NULL, showline = F, zeroline = F, gridcolor = '#ffff', ticklen = 2), 
    yaxis=list(domain = NULL, showline = F, zeroline = F, gridcolor = '#ffff', ticklen = 2)
  )

auto.splom
```

Correlation matrix. 

```{r}
cor(ISLR2::Auto[, 1:8])
```

Multivariate linear regression. 

```{r}
auto.dum <- ISLR2::Auto[, 1:8] %>% 
  mutate(American = if_else(origin == 1, 1, 0), 
         European = if_else(origin == 2, 1, 0)) %>% 
  select(-origin)

auto.lr <- lm(mpg ~ ., data = auto.dum)
summary(auto.lr)
```

Linear regression diagnostic plot. 

```{r}
par(mfrow = c(2, 2))
plot(auto.lr)
```

Stepwise regression. 

```{r}
auto.lr.inter <- lm(mpg ~ 1, data = auto.dum)
auto.lr.both <- stats::step(auto.lr.inter, scope = formula(auto.lr), direction = 'both', trace = 0)
summary(auto.lr.both)
```

weight, year, American. 

```{r}
auto.lr.both3 <- lm(mpg ~ weight + year + American, data = auto.dum)
summary(auto.lr.both3)
```

Successive orthogonalization. 

```{r}
auto.ortho <- auto.dum[, -1] %>% 
  mutate(x0 = 1, .before = 1) %>% 
  as.matrix() %>% 
  far::orthonormalization(basis = FALSE, norm = FALSE)

auto.lr.ortho.coef <- c()
for (i in 2:ncol(auto.ortho)) {
  auto.lr.res <- lm(auto.dum$mpg ~ auto.ortho[, i])
  auto.lr.ortho.coef[names(auto.dum)[i]] <- auto.lr.res$coefficients[2]
}

sort(auto.lr.ortho.coef)
```

cylinders, American, year. 

```{r}
auto.lr.ortho3 <- lm(mpg ~ cylinders + American + year, data = auto.dum)
summary(auto.lr.ortho3)
```

# Hitters

High salary. 

```{r}
plot(sort(ISLR2::Hitters$Salary))
```

Set threshold as 500. 

```{r}
hitters.class <- ISLR2::Hitters %>% 
  filter(!is.na(Salary)) %>% 
  mutate(Salary = if_else(Salary > 500, 1, 0), 
         League = if_else(League == 'A', 1, 0), 
         Division = if_else(Division == 'E', 1, 0), 
         NewLeague = if_else(NewLeague == 'A', 1, 0))
```

Stepwise. 

```{r}
hitters.lr.inter <- lm(Salary ~ 1, data = hitters.class)
hitters.lr.all <- lm(Salary ~ ., data = hitters.class)
hitters.lr.both <- stats::step(hitters.lr.inter, scope = formula(hitters.lr.all), direction = 'both', trace = 0)
summary(hitters.lr.both)
```

CHits, Hits. 

Linear regression. 

```{r}
hitters.lr <- lm(Salary ~ CHits + Hits, data = hitters.class)
summary(hitters.lr)
```

Logistic regression. 

```{r}
hitters.logistic <- glm(Salary ~ CHits + Hits, family = binomial(link = 'logit'), data = hitters.class)
summary(hitters.logistic)
```

Accurate rate. 

```{r}
hitters.pred.logistic <- hitters.class %>% 
  mutate(p = hitters.logistic$fitted.values, 
         Salary_p = if_else(p > 0.5, 1, 0), 
         acc = if_else(Salary == Salary_p, 1, 0))

(hitters.logistic.acc <- sum(hitters.pred.logistic$acc) / nrow(hitters.pred.logistic))

hitters.pred.lr <- hitters.class %>% 
  mutate(pred = hitters.lr$fitted.values, 
         Salary_p = round(pred), 
         acc = if_else(Salary == Salary_p, 1, 0))

(hitters.lr.acc <- sum(hitters.pred.lr$acc) / nrow(hitters.pred.lr))
```

Kernel density estimation. 

```{r}
hitters.error.select <- hitters.pred.logistic %>% 
  filter(acc == 0) %>% 
  select(CHits, Hits)

hitters.kde <- ks::kde(x = hitters.error.select, verbose = TRUE)
```

Plot kernel density estimation. 

```{r}
plot(hitters.kde, display = 'slice', cont = c(25, 50, 75, 100))
```

